Roster Review (Generic)

### 2019-07-22 rosterReview_generic.Rmd
Latest rosters, some adjustments to the fg_scrape methods

standings_projected %>% 
  mutate(team = fct_reorder(team, adj_sum_pos_zar)) %>% 
  ggplot(aes(team, adj_sum_pos_zar)) +
  geom_col() +
  geom_errorbar(aes(ymin=adj_sum_pos_zar-var_pos_zar, ymax=adj_sum_pos_zar+var_pos_zar), width = .5) +
  coord_flip()
```

>>>>

# FIXME pretty sure this error bar ain't right
standings_projected %>% 
  mutate(team = fct_reorder(team, adj_sum_pos_zar)) %>% 
  ggplot(aes(team, adj_sum_pos_zar)) +
  geom_col() +
  geom_errorbar(aes(ymin=adj_sum_pos_zar-var_pos_zar, ymax=adj_sum_pos_zar+var_pos_zar), width = .5) +
  coord_flip()
```
